The Galactic Delay-Time Distribution of Type Ia Supernovae:\\ A Chemical Evolution Perspective

### 2023-07-07 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{deluxetable*}{ll|ccccc}
\label{tab:results}
\tablehead{
    \colhead{DTD} & \colhead{SFH} & \colhead{[Fe/H] DF} & \colhead{[O/Fe] DF} & 
    \colhead{[Fe/H]--[O/Fe]} & \colhead{Age--[O/Fe]} & \colhead{Bimodality}
}
\startdata
Power law & Inside-out & \no & \meh & \meh & \no & \no \\
($\alpha=-1.1$) & Late-burst & \no & \no & \meh & \no & \no \\
 & Early-burst & \yes & \no & \no & \meh & \yes \\
 & Two-infall & \yes & \meh & \meh & \no & \no \\ 
\hline
Power law & Inside-out & \no & \no & \no & \no & \no \\
($\alpha=-1.4$) & Late-burst & \no & \no & \no & \no & \no \\
 & Early-burst & \meh & \no & \no & \no & \yes \\
 & Two-infall & \no & \no & \no & \no & \no \\ 
\hline
Exponential & Inside-out & \meh & \meh & \meh & \no & \no \\
($\tau=1.5$ Gyr) & Late-burst & \meh & \yes & \meh & \meh & \yes \\
 & Early-burst & \no & \no & \no & \meh & \yes \\
 & Two-infall & \yes & \meh & \meh & \meh & \yes \\ 
\hline
Exponential & Inside-out & \yes & \yes & \yes & \meh & \no \\
($\tau=3.0$ Gyr) & Late-burst & \meh & \yes & \yes & \yes & \yes \\
 & Early-burst & \meh & \no & \meh & \yes & \yes \\
 & Two-infall & \yes & \meh & \meh & \yes & \yes \\ 
\hline
Plateau & Inside-out & \meh & \yes & \yes & \meh & \no \\
($W=0.3$ Gyr) & Late-burst & \no & \yes & \yes & \meh & \yes \\
 & Early-burst & \meh & \meh & \no & \yes & \yes \\
 & Two-infall & \yes & \yes & \yes & \meh & \yes \\ 
\hline
Plateau & Inside-out & \yes & \yes & \yes & \meh & \no \\
($W=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
 & Early-burst & \meh & \meh & \meh & \yes & \yes \\
 & Two-infall & \yes & \yes & \yes & \yes & \yes \\ 
\hline
Prompt & Inside-out & \no & \no & \no & \no & \no \\
($t_{\rm max}=0.05$ Gyr) & Late-burst & \no & \no & \no & \no & \yes \\
 & Early-burst & \yes & \no & \no & \meh & \yes \\
 & Two-infall & \meh & \meh & \no & \no & \no \\ 
\hline
Triple system & Inside-out & \yes & \yes & \yes & \yes & \no \\
($t_{\rm max}=1.0$ Gyr) & Late-burst & \no & \yes & \yes & \yes & \yes \\
 & Early-burst & \meh & \meh & \meh & \yes & \yes \\
 & Two-infall & \yes & \meh & \yes & \yes & \yes \\
\enddata
\end{deluxetable*}

>>>>

\variable{output/summary_table.tex}
